---
output:
  md_document:
    variant: markdown_github
---

# Purpose

Purpose of this work folder.

Ideally store a minimum working example data set in data folder.

Add binary files in bin, and closed R functions in code. Human Readable settings files (e.g. csv) should be placed in settings/


```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
library(readr)
```


First, we start by importing the data:
```{r}
data <- read_csv("D:\\User folders\\Documents\\2023 Stellenbosch MCom (Economics)\\Semester 1\\Data Science for Economics and Finance 871\\Data_Science_Project\\Project\\data\\academy_awards.csv")
```

Now we want to create a dataframe of all best picture winners, and add values for whether they were nominated for any other awards.
```{r}

```

